A 38 Million Year Old Mini-Neptune in the Kepler Field

### 2021-10-01 paper/ms.tex
update ms
* Improve phased quartile appendix discussion
* Improve RM appendix discussion
* Push updated RM plots

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f4b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities acquired using Keck/HIRES during the transit of
			2021 Aug 7, observed simultaneously with MuSCAT3.}  Shaded bands
		show 2-$\sigma$ model uncertainties.  The photometric transit
		depths are consistent across the {\it griz} bandpasses.  The
		best-fitting model in the top panel includes the RM effect and a quadratic trend
		in time.  The radial velocity scatter
		between exposures ($\sigma_{\rm RV}\approx50$\ms) prevented us from detecting the RM
		effect.
		\label{fig:ground}
	}
\end{figure}

A third supporting line of evidence for the planetary interpretation
exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:ground}).  Fitting
the MuSCAT3 photometry with a model that lets the transit depths vary
across each bandpass, we find {\it griz} depths consistent with the
Kepler depth at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The
MuSCAT3 observations also suggest a transit duration $17.4\pm3.6\ {\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether the transit duration is indeed
changing.  For our RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While the velocities are marginally more
consistent with a prograde or polar orbit than a retrograde orbit, the
spot-corrected exposure-to-exposure scatter ($\sigma_{\rm RV}\approx
50$\ms) is larger than the expected velocity anomaly
($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$).  We are therefore
not in a position to claim a spectroscopic detection of the RM effect,
nor to quantify the stellar obliquity.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.7\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
		its uncertainty.  \pn\ is shown with a star.  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2021
		Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit models and residuals, binned by local slope of the
    raw light curve}.  Local linear slopes are measured over each
    transit window (144 transits total).  Four outlier transits were
    removed, leaving 140 transits.  These were then divided into
    quartiles, so that each panel shows 35 transits binned together.
    The exact light curve slopes are listed in the lower left panels.
    Representative uncertainties for the black points (binned at 20
    minute intervals) are shown in the lower right of each panel.  A
    similar transit asymmetry to that shown in Figure~\ref{fig:lc}
    seems to be present in three of the four bins.
		\label{fig:phaseslope}
	}
\end{figure}

As a means of exploring the robustness of the transit asymmetry,
Figures~\ref{fig:phasequarter},~\ref{fig:phaseyear},
and~\ref{fig:phaseslope} show the Kepler data binned in three ways:
over quarters, years, and local slope quartiles.  Over quarters
(Figure~\ref{fig:phasequarter}), Quarter 6 shows the strongest asymmetry
out of any quarter: a deviation of about 3\,ppt from expectation.
Quarter 7 shows an anomaly at roughly the same transit phase.  Year 2
correspondingly shows the strongest anomaly out of any year in
Figure~\ref{fig:phaseyear}; the asymmetry is visually apparent however
in each of Years 2, 3, and 4.
Binned by local slope quartiles (Figure~\ref{fig:phaseslope}), the
asymmetry is visually present in three of the four quartiles: the only
bin for which it appears to not be present is ${\rm d}f/{\rm
d}t\in[0.001,0.033]\,{\rm ppt\,day}^{-1}$.

We considered four possible interpretations of the transit asymmetry:
gravity darkening, transit timing variations, spot-crossing events,
and a persistent asymmetric dusty outflow.

@@

We monitored \sn\ with Keck/HIRES before, during, and after transit on
the night of 2021 Aug 7.  We used the iodine cell for wavelength
calibration\footnote{We considered a line-profile based analysis in
the regions without iodine, but the line profile stability of HIRES
precludes such an approach.}, extracted the 1-D spectra using the
standard California Planet Survey pipeline \citep{howard_cps_2010},
and measured the velocities by cross-correlating against a template
found via spectral classification with \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}.  The airmass ranged between 1.1 and 2.2 from the
start through the end of observations; the seeing ranged from
$1\farcs1$ at the beginning to $1\farcs5$ at the end.  We also
simultaneously observed across {\it griz} bands using MuSCAT3 at
Faulkes Telescope North on Maui, HI.

Figure~\ref{fig:ground} shows the results.  The
MuSCAT3 photometry shows the expected starspot trend, along with the
transit and what is likely a chromatic starspot crossing event at
${\rm JD} - 2459433 = 0.955$.  The radial velocities decrease by
800\ms\ over the six hour window.  A $\approx50$\ms\  increase in RV
is seen shortly after the expected ingress time.

Overall, we expect the dominant trends in both the photometry and
radial velocities to be caused by starspots on the stellar photosphere
rotating into and out of view.  The plasma in the leading and receding
limbs of the stellar disk has an apparent line-of-sight velocity of
$\pm 20$\kms.  Over 10\% of a rotation cycle ($P_{\rm
rot}=2.6\,{\rm days}$), spots near these limbs come into and out of
view, modulate the stellar velocity profile, and can thereby produce
the overall 800\ms\ trend.  The Ca HK and H$\alpha$ emission
profiles support this interpretation;
Figure~\ref{fig:rvactivity} shows that each line gradually decreases in
intensity over the course of the six hour sequence.
The overall RVs are also heavily correlated against the S-indices
derived from the Ca HK lines.

The expectation however is for the starspot-induced signals to be smooth,
at worst with contributions at $0.5\,P_{\rm rot}$ or $0.25\,P_{\rm
rot}$ \citep{klein_simulated_2020}.  We therefore fitted the RVs using
the \citet{hirano_analytic_2010,hirano_2011} models for the
Rossiter-McLaughlin (RM) effect, and allowed for an optional linear
and quadratic trend in time to fit the 800\ms\ spot-induced trend.  We
followed the methodology developed by \citet{stefansson_2020}.  We
allowed the sky-projected obliquity, the projected stellar equatorial
velocity, and the Gaussian dispersion of the spectral lines to vary,
and fixed the limb-darkening using the $V$-band tabulation from
\citet{claret_gravity_2011}.  We assumed a Gaussian prior on $v\sin i$ and
$a/R_\star$ from Table~\ref{tab:starparams}, and also allowed for a
white-noise jitter term to be added in quadrature to the measurement
uncertainties.

The quadratic model with the RM effect is shown in
Figure~\ref{fig:ground}; the jitter term is incorporated in the
model uncertainties, but not the plotted measurement uncertainties.
The plotted measurement uncertainties are the internal uncertainties
on the RVs ($\approx 15\,{\rm m\,s}^{-1}$), and are dominated by the
$v\sin i$ broadening.  However, between exposures, the RVs show
significant additional scatter that is not captured by the slow quadratic
trend.  The white-noise jitter for this
particular model is $\sigma_{\rm RV} = 50^{+11}_{-8}$\ms, which is
larger than the expected RM anomaly of $\Delta v_{\rm RM}
\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
\approx 20\,{\rm m\,s}^{-1}$.

The presence of this additional scatter prevents a convincing detection of
the RM effect.  The reason can be understood via
model comparison.  If we compare the model with a quadratic trend and
the RM effect against a model with a
linear trend and the RM effect, or even a model with no RM effect at
all, then the respective Bayesian Information Criterion (BIC) values
are as follows.
% from logs/rm_freejitter_FINAL.log
\begin{align}
  {\rm BIC} &= 251.7  \quad ({\rm Quadratic+RM}) \nonumber \\
  {\rm BIC} &= 257.7  \quad ({\rm Linear+RM}) \nonumber \\
  {\rm BIC} &= 247.1  \quad ({\rm Only\ Quadratic}).
\end{align}
There is therefore no evidence to prefer the model with the RM effect
against a model that only accounts for the stellar variability.
The ``only quadratic'' model does particularly well because it can
inflate the jitter term to account for scatter during
the transit (even if the scatter contains astrophysics!), and it has fewer free parameters.  However, we cannot
justify a physical prior on the jitter term, because we do not
understand the origin of the exposure-to-exposure scatter.  As noted
above, the velocity deviations from starspots are expected to have
contributions at the stellar rotation frequency, or harmonics thereof.
This jitter is present on the exposure timescale (15 minutes), which
is only 0.4\% of the stellar rotation period; it is not obvious that
starspots would be the culprit.

The amplitude of both the spot-induced trend and the jitter are larger
than recent comparable measurements in systems such as AU~Mic
\citep{palle_transmission_2020}, DS~Tuc
\citep{montet_young_2020,zhou_well_2020} and TOI~942
\citep{wirth_2021_toi942}.  One possible explanation for the jitter is
that it is astrophysical in origin, and that it is caused by some
novel process operating on the surface of Kepler 1627A.  Another
possibility is that our RV analysis underestimates our measurement
uncertainties; the S/N per resolution element for each of our spectra
was 70 to 80, which is somewhat low for deriving high-precision
velocities.  In addition, the rapid rotation of the star could affect
accuracy of the uncertainties from the velocity extraction.
Observations at higher precision are necessary to distinguish these
two possibilities, and remain worthwhile as a means toward clarifying
the orbital geometry of \pn.

>>>>

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{f4b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radial velocities acquired using Keck/HIRES during the transit of
			2021 Aug 7, observed simultaneously with MuSCAT3.}  Shaded bands
		show 2-$\sigma$ model uncertainties.  The photometric transit
		depths are consistent across the {\it griz} bandpasses.  The
		best-fitting model in the top panel includes the RM effect and a quadratic trend
		in time to model the spot-induced $\approx$\,$250$\ms\ trend (see Appendix~\ref{app:rm}).  The radial velocity jitter
		over the 15~minute exposure timescale ($\sigma_{\rm RV}\approx30$\ms) prevented us from detecting the RM
		effect.
		The RV variations are strongly correlated with varying emission in the Ca H and K lines (middle panel).
		\label{fig:ground}
	}
\end{figure}

A third supporting line of evidence for the planetary interpretation
exists, though we consider it less definitive than the stellar
density and TTV-local slope correlation.  We observed a transit of
\pn\ on the night of 2021 Aug 7 simultaneously with Keck/HIRES and
MuSCAT3.  We scheduled the observations using the ephemeris of
\citet{holczer_transit_2016}.  Although we did not detect the
Rossiter-McLaughlin (RM) anomaly, the multi-band MuSCAT3 light curves
show the transit (Figure~\ref{fig:ground}).  Fitting
the MuSCAT3 photometry with a model that lets the transit depths vary
across each bandpass, we find {\it griz} depths consistent with the
Kepler depth at 0.6, 0.3, 0.3, and 1.1-$\sigma$ respectively.  The
MuSCAT3 observations also suggest a transit duration $17.4\pm3.6\ {\rm
minutes}$ shorter than the Kepler transits; further photometric
follow-up could help confirm whether the transit duration is indeed
changing.  For our RM analysis, the details are discussed in
Appendix~\ref{app:rm}.  While the velocities are marginally more
consistent with a prograde or polar orbit than a retrograde orbit, the
spot-corrected exposure-to-exposure scatter ($\sigma_{\rm RV}\approx
30$\ms) is comparable to the expected velocity anomaly assuming an
aligned orbit ($\Delta v_{\rm RM}\approx 20\,{\rm m\,s}^{-1}$).  We
are therefore not in a position to claim a spectroscopic detection of
the RM effect, nor to quantify the stellar obliquity.

@@

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.75\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
		Planets younger than a gigayear with ${\rm \tau}/\sigma_{\tau} >
		3$ are emphasized, where $\tau$ is the age and $\sigma_{\tau}$ is
		its uncertainty.  \pn\ is shown with a star.  The large sizes of
		the youngest transiting planets could be explained by their
		primordial atmospheres not yet having evaporated; direct
		measurements of the atmospheric outflows or planetary masses would
		help to confirm this expectation.  Selection effects may also be
		important.  Parameters are from the NASA Exoplanet Archive (2021
		Sept 15).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f9.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit models and residuals, binned by quartiles in the local slope of the
    light curve}.  
    Representative uncertainties for the black points (binned at 20
    minute intervals) are shown in the lower right of each panel.  A
    similar transit asymmetry to that shown in Figure~\ref{fig:lc}
    seems to be present in three of the four bins.
    \vspace{-0.5cm}
		\label{fig:phaseslope}
	}
\end{figure}
\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f9b.pdf}
	\end{center}
	\vspace{-0.7cm}
	\caption{
    {\bf Transit models and residuals, binned by quartiles of transit
    timing variations}.  The data are otherwise the same as in
    Figure~\ref{fig:phaseslope}.
		\label{fig:phasettv}
	}
\end{figure}

\subsection{Is the Transit Asymmetry Robust?}

As a means of exploring the robustness of the transit asymmetry,
Figures~\ref{fig:phasequarter},~\ref{fig:phaseyear},~\ref{fig:phaseslope},
and~\ref{fig:phasettv} show the Kepler data binned in four ways:
over Kepler quarters, Julian years, quartiles of local slope, and quartiles of
transit timing variation.  Over Kepler quarters
(Figure~\ref{fig:phasequarter}), Quarter 6 shows the strongest asymmetry: a deviation of about 3\,ppt from expectation.
Quarter 7 shows an anomaly at roughly the same transit phase.  Year 2
correspondingly shows the strongest anomaly out of any year in
Figure~\ref{fig:phaseyear}; the asymmetry is visually apparent however
in each of Years 2, 3, and 4.

To bin by quartiles in local slope and TTV, we used our measurements
of the local linear slopes in each of the observed transit windows
(144 transits total).  Four outlier transits were removed, leaving 140
transits.  These were then divided into quartiles, so that each panel
shows 35 transits binned together.  The exact light curve slope and
TTV intervals are listed in the lower left panels of
Figures~\ref{fig:phaseslope} and~\ref{fig:phasettv}.  Binned by local
slope quartiles (Figure~\ref{fig:phaseslope}), the asymmetry is
visually present in three of the four quartiles: the only bin in
which it does not appear is ${\rm d}f/{\rm
d}t\in[0.001,0.033]\,{\rm ppt\,day}^{-1}$.  The corresponding bins in TTV
(largest TTV corresponding to smallest ${\rm d}f/{\rm d}t$)
show the same asymmetries, though with somewhat greater scatter
(Figure~\ref{fig:phasettv}).

Within the theory presented by \citet{mazeh_time_2015}, unresolved
starspot crossings cause the correlation between TTVs and the local
light curve slope (Figure~\ref{fig:corr}).  In this model, we would
expect the light curves with the most negative local slopes
to have the largest positive TTVs, due to spot crossing events during the latter
half of transit.  The lower-right panel of Figure~\ref{fig:phasettv}
and upper-left panel of Figure~\ref{fig:phaseslope} agree with this
expectation.  However, we would also expect the sign of the effect to
reverse when considering the most positive local slopes, and the most
negative TTVs.  The upper-left panel of Figure~\ref{fig:phasettv} and
lower-right panel of Figure~\ref{fig:phaseslope} contradict this
expectation: the residual in both cases maintains the same
parity!  On the one hand, this shows us that the residual is not
strongly dependent on the local light curve slope, which mitigates the
possibility that it might be an artifact of our detrending methods.
On the other, it raises the question of whether
unresolved starspot crossings are indeed the root cause of the correlation shown in
Figure~\ref{fig:corr}.

% FIXME: KM to discuss injection recovery...

\subsection{Possible Explanations}

Since the transit asymmetry seems robust against most methods of
binning the data, we considered four possible astrophysical
interpretations: gravity darkening, transit timing variations,
spot-crossing events, and a persistent asymmetric dusty outflow.

@@

We monitored \sn\ with Keck/HIRES before, during, and after transit on
the night of 2021 Aug 7.  We used the iodine cell for wavelength
calibration\footnote{We considered a line-profile based analysis in
the regions without iodine, but the line profile stability of HIRES
precludes such an approach.}, and extracted the 1-D spectra using the
standard California Planet Survey pipeline \citep{howard_cps_2010}.
The airmass ranged between 1.1 and 2.2 from the
start through the end of observations; the seeing ranged from
$1\farcs1$ at the beginning to $1\farcs5$ at the end.  We also
simultaneously observed across {\it griz} bands using MuSCAT3 at
Faulkes Telescope North on Maui, HI.

We considered two approaches to measuring the velocities: in the
first, hereafter ``Method 1'', we cross-correlated against a template found via
spectral classification with \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}.  In ``Method 2'', we used a high S/N template of
V1298~Tau.  Although V1298 Tau is cooler than Kepler~1627A by
$\approx$500\,K, it has a comparable amount of line-broadening ($v\sin
i = 23$\kms), and a comparable level of stellar activity.  The mean
and standard deviation of the internal RV uncertainties averaged over
all epochs were $16.2\pm1.1$\ms\ from Method 1, and $12.6\pm0.6$\ms\ from Method 2.
The corresponding time-averaged reduced $\chi^2$ from the template
match was $1.57\pm0.04$ (Method 1) and $1.30\pm0.02$ (Method 2).
Given these diagnostics, we adopted the velocities from the second
approach.

Figure~\ref{fig:ground} shows the results.  The
MuSCAT3 photometry shows the expected starspot trend, along with the
transit and what is likely a chromatic starspot crossing event at
${\rm JD} - 2459433 = 0.955$.  The radial velocities decrease by
$\approx$250\ms\ over the six hour window.  
This decrease in RV is heavily with a decrease in the S-indices
derived from the Ca HK lines.
One outlying RV point is apparent shortly before egress; it is
temporally coincident with an outlying value in the S-index time series.

Overall, we expect the dominant trends in both the photometry and
radial velocities to be caused by starspots on the stellar photosphere
rotating into and out of view.  The plasma in the leading and receding
limbs of the stellar disk has an apparent line-of-sight velocity of
$\pm 20$\kms.  Over 10\% of a rotation cycle ($P_{\rm
rot}=2.6\,{\rm days}$), spots near these limbs come into and out of
view, modulate the stellar velocity profile, and can thereby produce
the overall $\approx$250\ms\ trend.  The Ca HK and H$\alpha$ emission
profiles support this interpretation;
Figure~\ref{fig:rvactivity} shows that each line gradually decreases in
intensity over the course of the six hour sequence.

The expectation however is for the starspot-induced signals to be smooth,
at worst with contributions at $0.5\,P_{\rm rot}$ or $0.25\,P_{\rm
rot}$ \citep{klein_simulated_2020}.  We therefore fitted the RVs using
the \citet{hirano_analytic_2010,hirano_2011} models for the
Rossiter-McLaughlin (RM) effect, and allowed for an optional linear
and quadratic trend in time to fit the $\approx$250\ms\ spot-induced trend.  We
followed the methodology developed by \citet{stefansson_2020}.  We
allowed the sky-projected obliquity, the projected stellar equatorial
velocity, and the Gaussian dispersion of the spectral lines to vary,
and fixed the limb-darkening using the $V$-band tabulation from
\citet{claret_gravity_2011}.  We assumed a Gaussian prior on $v\sin i$ and
$a/R_\star$ from Table~\ref{tab:starparams}, and also allowed for a
white-noise jitter term to be added in quadrature to the measurement
uncertainties.
We used the 15\,minute exposure time when numerically evaluating the
model.

The quadratic model with the RM effect is shown in
Figure~\ref{fig:ground}; the jitter term is incorporated in the
model uncertainties, but not the plotted measurement uncertainties.
The plotted measurement uncertainties are the internal uncertainties
on the RVs ($\approx 13\,{\rm m\,s}^{-1}$), and are dominated by the
$v\sin i$ broadening.  However, between exposures, the RVs show
significant additional scatter that is not captured by the slow quadratic
trend.  The white-noise jitter for this
particular model is $\sigma_{\rm RV} = 27^{+6}_{-5}$\ms, which is
comparable to the expected RM anomaly of $\Delta v_{\rm RM}
\approx f_{\rm LD} \cdot \delta \cdot v\sin i \cdot \sqrt{1-b^2}
\approx 20\,{\rm m\,s}^{-1}$, assuming a perfectly aligned orbit.

The presence of this additional scatter prevents a convincing detection of
the RM effect.  The reason can be understood via
model comparison.  If we compare the model with a quadratic trend and
the RM effect against a model with a
linear trend and the RM effect, or even a model with no RM effect at
all, then the respective Bayesian Information Criterion (BIC) values
are as follows.
% from rm_TEMPLATE_V1298TAU_quadraticfreejitter_v0.log and
% rm_TEMPLATE_V1298TAU_v1_linearfreejitter_trendonlyfreejitter.log
\begin{align}
  {\rm BIC} &= 227.1  \quad ({\rm Quadratic+RM}) \nonumber \\
  {\rm BIC} &= 231.1  \quad ({\rm Linear+RM}) \nonumber \\
  {\rm BIC} &= 221.4  \quad ({\rm Only\ Quadratic}).
\end{align}
There is therefore no evidence to prefer the model with the RM effect
against a model that only accounts for the stellar variability.  The
``only quadratic'' model does particularly well because it can inflate
the jitter term to account for scatter during the transit (even if the
scatter contains astrophysics!), and it has fewer free parameters.
However, we cannot justify a physical prior on the jitter term,
because we do not understand the origin of the exposure-to-exposure
scatter.  As noted above, the velocity deviations from starspots are
expected to have contributions at the stellar rotation frequency, or
harmonics thereof.  This jitter is present on the exposure timescale
(15 minutes), which is only 0.4\% of the stellar rotation period; it
is not obvious that starspots would be the culprit.

The amplitude of both the spot-induced trend and the jitter are
somewhat larger than recent comparable measurements in systems such as
AU~Mic \citep{palle_transmission_2020}, DS~Tuc
\citep{montet_young_2020,zhou_well_2020} and TOI~942
\citep{wirth_2021_toi942}.  One possible explanation for the jitter is
that it is astrophysical in origin, and that it is caused by some
novel process operating on the surface of Kepler 1627A.  Another
possibility is that our RV analysis underestimates our measurement
uncertainties; in order to achieve the requisite time-sampling the S/N
per resolution element in our spectra was 70 to 80, which is lower
than desired for deriving high-precision velocities.  In addition, the
rapid rotation of the star could affect accuracy of the uncertainties
from the velocity extraction.  Observations at higher S/N are
necessary to distinguish these two possibilities, and remain
worthwhile in order to clarify the orbital geometry of \pn.  Useful
next steps would include transit observations with a stabilized
optical spectrograph, or potentially also observations in the
near-infrared \citep[{\it e.g.},][]{feinstein_halpha_2021}.
